Collapse of tall granular columns in fluid

### 2017-02-07 paper.tex
Changed long sentence

\section{Numerical set-up}
In this study, a 2D poly-disperse system ($d_{max} / d_{min} = 1.8$) of
circular discs in fluid was used to understand the behaviour of granular
flows on slopes (see~\cref{fig:geometry}).
The soil column was modelled using 2500 discs of density
2650~\si{\kilogram\per\meter\cubed} and a contact friction angle of
26\si{\degree}.  The  collapse of the column was simulated inside a fluid
with a density of 1000~\si{\kilogram\per\meter\cubed} and a kinematic viscosity
of $1 \times 10^{-6}$~\si{\meter\squared\per\second}. The fluid was modelled
with 5 to 9 million LB nodes. GPU computing was used to simulate the problem.
The choice of a 2D geometry has the advantage of cheaper computational
effort than a 3D case, makeing it feasible to simulate very large systems.
A granular column of aspect ratio `\textit{a}' of 6 was used. A hydrodynamic
radius of \textit{r} = 0.85 \textit{R} is adopted. Dry analyses were also
performed to study the effect of hydrodynamic forces on the run-out distance.
The collapse of a tall granular column on slopes of 0\si{\degree},
2.5\si{\degree}, 5\si{\degree} and 7.5\si{\degree} are studied.

@@

\subsection{Effect of slope angle}
In order to understand the influence of slope angles on the run-out behaviour, 
the collapse of a granular column with an initial aspect ratio of 6 is 
performed on slopes of 0\si{\degree}, 2.5\si{\degree}, 5\si{\degree} and 
7.5\si{\degree}. The run-out evolution with time for different slope angles are 
presented in~\cref{fig:Runout_a6_slope}. The run-out distance increases with 
increase in the slope angle, however the run-out distance in the fluid is 
significantly shorter than the dry condition. The slow evolution of run-out in 
the submerged condition is due to the delay in the dissipation of large 
negative pore-pressures developed during the initial stage of the collapse. The 
formation of eddies during the flow indicates that most of the potential energy 
gained during the free-fall is dissipated through viscous drag and turbulence. 
This effect predominates over the hydroplaning that is observed during 
the flow resulting in a shorter run-out distance in the case of fluid. The 
evolution of the normalised height with time (\cref{fig:Height_a6_slope}) for 
collapse on different slope angles indicates that the 
amount of material destabilised in fluid is less than the dry conditions due to 
the drag forces experienced by the grains, which retards the quantity and the 
rate of collapse.

>>>>

\section{Numerical set-up}
In this study, a 2D poly-disperse system ($d_{max} / d_{min} = 1.8$) of
circular discs in fluid was used to understand the behaviour of granular
flows on slopes (see~\cref{fig:geometry}).
The soil column was modelled using 2500 discs of density
2650~\si{\kilogram\per\meter\cubed} and a contact friction angle of
26\si{\degree} and a mean packing fraction of $\approx 0.82$.
The  collapse of the column was simulated inside a fluid
with a density of 1000~\si{\kilogram\per\meter\cubed} and a kinematic viscosity
of $1 \times 10^{-6}$~\si{\meter\squared\per\second}. The fluid was modelled
with 5 to 9 million LB nodes. GPU computing was used to simulate the problem.
The choice of a 2D geometry has the advantage of cheaper computational
effort than a 3D case, makeing it feasible to simulate very large systems.
A granular column of aspect ratio `\textit{a}' of 6 was used. A hydrodynamic
radius of \textit{r} = 0.85 \textit{R} is adopted. Dry analyses were also
performed to study the effect of hydrodynamic forces on the run-out distance.
The collapse of a tall granular column on slopes of 0\si{\degree},
2.5\si{\degree}, 5\si{\degree} and 7.5\si{\degree} are studied.

@@

\subsection{Effect of slope angle}
In order to understand the influence of slope angles on the run-out behaviour, 
the collapse of a granular column with an initial aspect ratio of 6 is 
performed on slopes of 0\si{\degree}, 2.5\si{\degree}, 5\si{\degree} and 
7.5\si{\degree}. The run-out evolution with time for different slope angles are 
presented in~\cref{fig:Runout_a6_slope}. The run-out distance increases with 
increase in the slope angle, however the run-out distance in the fluid is 
significantly shorter than the dry condition. The slow evolution of run-out in 
the submerged condition is due to the delay in the dissipation of large 
negative pore-pressures developed during the initial stage of the collapse. The 
formation of eddies during the flow indicates that most of the potential energy 
gained during the free-fall is dissipated through viscous drag and turbulence. 
This effect predominates over the hydroplaning that is observed during 
the flow resulting in a shorter run-out distance in the case of fluid. The 
evolution of the normalised height with time (\cref{fig:Height_a6_slope}) for 
collapse on different slope angles indicates that the 
amount of material destabilised in fluid is less than the dry conditions.
This is due to the drag forces experienced by the grains, which retards the
quantity and the rate of collapse.
